---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
##===================================
## Create Seurat object from raw data

```{r}
library(Seurat)
library(ggplot2)
library(dplyr)
library(plyr)
library(RColorBrewer) # good sets of color to replace default Seurat colors for better contrast
```

```{r}
## load expression matrix and meta data from Dmitry
load("C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Hs_LCM_Seurat_export_slim.RData")
```

#============================================================
## Data intergration from different batchs/donors_start

```{r}
# splitting dataset into samples for anchor integration
counts.N2.RL5 <- HS.counts.raw[,grepl("N2-RL5", colnames(HS.counts.raw))]
counts.N2.RT1 <- HS.counts.raw[,grepl("N2-RT1", colnames(HS.counts.raw))]
counts.N3.RL2 <- HS.counts.raw[,grepl("N3-RL2", colnames(HS.counts.raw))]
counts.N3.RT1 <- HS.counts.raw[,grepl("N3-RT1", colnames(HS.counts.raw))]
counts.N4.RL3 <- HS.counts.raw[,grepl("N4-RL3", colnames(HS.counts.raw))]
counts.N4.RT1 <- HS.counts.raw[,grepl("N4-RT1", colnames(HS.counts.raw))]

cdl.1 <- list('N2.RL5'=as(as.matrix(counts.N2.RL5),'dgCMatrix'),
              'N2.RT1'=as(as.matrix(counts.N2.RT1),'dgCMatrix'),
              'N3.RL2'=as(as.matrix(counts.N3.RL2),'dgCMatrix'),
              'N3.RT1'=as(as.matrix(counts.N3.RT1),'dgCMatrix'),
              'N4.RL3'=as(as.matrix(counts.N4.RL3),'dgCMatrix'),
              'N4.RT1'=as(as.matrix(counts.N4.RT1),'dgCMatrix')
)
```

```{r}
# removing 'GLIA.DUBLETS' cells from all samples, GLIA, DUBLTETS are annotated by Dmitry based on his analysis
for (i in 1:length(cdl.1)){
  cdl.1[[i]] <- cdl.1[[i]][,!(colnames(cdl.1[[i]]) %in% cells.GLIA.DUBL)]
}

```

```{r}
# creating a list of seurat objects corresponding to samples
Seurat.list <- NULL
for (i in 1:length(cdl.1)){
  Seurat.list[[i]] <- CreateSeuratObject(counts = cdl.1[[i]], min.cells = 2, min.features = 1000)
}
```

```{r}
#choosing parameters of integration
n.var.features <- 4500
n.integr.features <- 3000
nn.pcs <- 25
```

```{r}
#generating title for future plots to remember which parameters were used
title.w.param <- paste('UMAP-', n.integr.features, '\n n.var.features=', n.var.features,
                       '\n dim =', nn.pcs)
```

```{r}
#normalizing & finding variable genes for individual seurat objects
for (i in 1:length(Seurat.list)) {
  Seurat.list[[i]] <- NormalizeData(Seurat.list[[i]], verbose = T)
  Seurat.list[[i]] <- FindVariableFeatures(Seurat.list[[i]], selection.method = "vst",
                                           nfeatures = n.var.features, verbose = T)
}
```
```{r}
# integration
features <- SelectIntegrationFeatures(object.list = Seurat.list, nfeatures = n.integr.features)
S.anchors <- FindIntegrationAnchors(object.list = Seurat.list, anchor.features = features)
```

```{r}
# integration
to_integrate <- c(row.names(HS.counts.raw))
#to_integrate <- Reduce(intersect, lapply(S.anchors@object.list, rownames))
Seurat.integr <- IntegrateData(anchorset = S.anchors, k.weight = 80, features.to.integrate = to_integrate)
```

#============================================================
## Data intergration from different donors_end



#============================================================
## Clustering_start

```{r}
# removing process intermediates 
rm(list = ls()[grep("counts.N|S.anchor|Seurat.list", ls(), invert = F)])
```

```{r}
# clustering 
DefaultAssay(Seurat.integr) <- "integrated"
Seurat.integr <- ScaleData(Seurat.integr, verbose = T, features)
Seurat.integr <- RunPCA(Seurat.integr, verbose = F)
Seurat.integr <- RunUMAP(Seurat.integr, dims = 1:nn.pcs, verbose = T)
Seurat.integr <- FindNeighbors(Seurat.integr, dims = 1:nn.pcs, verbose = T)
#FindClusters(Seurat.integr, resolution =1.2, verbose = T)
#DimPlot(test, group.by = "seurat_clusters", cols = XX.color.Paired.to.22.v2, label = T)
```

```{r}
#resolution = 4.5 for
Seurat.integr <- FindClusters(Seurat.integr, resolution =3.4, verbose = T)
DimPlot(Seurat.integr, group.by = "seurat_clusters", label = T)
```
#============================================================
## Clustering_end



#===========================================================
## Import cluster annotation and metadata from previous documents_start

```{r}
# importing clusters annotation from Meta df to new seurat object
# ===========================================
Meta.1066.wo.glia <- Meta.fused[!(rownames(Meta.fused) %in% cells.GLIA.DUBL),]
cl.conserv <- Meta.1066.wo.glia$cl.conserv
cl.HC.LC.split <-Meta.1066.wo.glia$cl.HC.LC.split
cl.Ab.split.3 <- Meta.1066.wo.glia$cl.Ab.split.3
cl.Ab.split.4 <- Meta.1066.wo.glia$cl.Ab.split.4

names(cl.conserv) <- rownames(Meta.1066.wo.glia)
names(cl.HC.LC.split) <- rownames(Meta.1066.wo.glia)
names(cl.Ab.split.3) <- rownames(Meta.1066.wo.glia)
names(cl.Ab.split.4) <- rownames(Meta.1066.wo.glia)

Seurat.integr$cl.conserv <- cl.conserv
Seurat.integr$cl.HC.LC.split <- cl.HC.LC.split
Seurat.integr$cl.Ab.split.3 <- cl.Ab.split.3
Seurat.integr$cl.Ab.split.4 <- cl.Ab.split.4
# ==================================================
```

```{r}
##==================================================
# importing clusters annotation from Meta df to new seurat object
# ===========================================
Meta.1066.wo.glia <- Meta.fused[!(rownames(Meta.fused) %in% cells.GLIA.DUBL),]
cl.conserv <- Meta.1066.wo.glia$cl.conserv

diameter <-Meta.1066.wo.glia$diameter
names(diameter) <- rownames(Meta.1066.wo.glia)

donor <-Meta.1066.wo.glia$donor
names(donor) <- rownames(Meta.1066.wo.glia)

drg_level <-Meta.1066.wo.glia$drg_level
names(drg_level) <- rownames(Meta.1066.wo.glia)

drg_location <-Meta.1066.wo.glia$drg_location
names(drg_location) <- rownames(Meta.1066.wo.glia)

batch <-Meta.1066.wo.glia$batch
names(batch) <- rownames(Meta.1066.wo.glia)

Seurat.integr$diameter <- diameter

Seurat.integr$drg_level <- drg_level

Seurat.integr$drg_location <- drg_location

Seurat.integr$batch <- batch

Seurat.integr$donor <- donor

# ==================================================
```
#===========================================================
## Import cluster annotation and metadata from previous documents_end



#===========================================================
## Assign cluster into functional groups_start

```{r}
## Get cell identity of each Seurat cluster
cl0_cell <- row.names(Seurat.integr[[]][Seurat.integr[[]]$seurat_clusters=='0',])
cl1_cell <- row.names(Seurat.integr[[]][Seurat.integr[[]]$seurat_clusters=='1',])
cl2_cell <- row.names(Seurat.integr[[]][Seurat.integr[[]]$seurat_clusters=='2',])
cl3_cell <- row.names(Seurat.integr[[]][Seurat.integr[[]]$seurat_clusters=='3',])
cl4_cell <- row.names(Seurat.integr[[]][Seurat.integr[[]]$seurat_clusters=='4',])
cl5_cell <- row.names(Seurat.integr[[]][Seurat.integr[[]]$seurat_clusters=='5',])
cl6_cell <- row.names(Seurat.integr[[]][Seurat.integr[[]]$seurat_clusters=='6',])
cl7_cell <- row.names(Seurat.integr[[]][Seurat.integr[[]]$seurat_clusters=='7',])
cl8_cell <- row.names(Seurat.integr[[]][Seurat.integr[[]]$seurat_clusters=='8',])
cl9_cell <- row.names(Seurat.integr[[]][Seurat.integr[[]]$seurat_clusters=='9',])
cl10_cell <- row.names(Seurat.integr[[]][Seurat.integr[[]]$seurat_clusters=='10',])
cl11_cell <- row.names(Seurat.integr[[]][Seurat.integr[[]]$seurat_clusters=='11',])
cl12_cell <- row.names(Seurat.integr[[]][Seurat.integr[[]]$seurat_clusters=='12',])
cl13_cell <- row.names(Seurat.integr[[]][Seurat.integr[[]]$seurat_clusters=='13',])
cl14_cell <- row.names(Seurat.integr[[]][Seurat.integr[[]]$seurat_clusters=='14',])
cl15_cell <- row.names(Seurat.integr[[]][Seurat.integr[[]]$seurat_clusters=='15',])
cl16_cell <- row.names(Seurat.integr[[]][Seurat.integr[[]]$seurat_clusters=='16',])
cl17_cell <- row.names(Seurat.integr[[]][Seurat.integr[[]]$seurat_clusters=='17',])
cl18_cell <- row.names(Seurat.integr[[]][Seurat.integr[[]]$seurat_clusters=='18',])
```

```{r}
## manually assign cluster based on UMAP
## Select cells based on UMAP

#Cells_selected <- CellSelector(a)
#Print(Cells_selected)
```

```{r}
## cl.TRPM8 and cl.CLTMR assignment are based on UMAP, Un.Gi and Ab.LTMR assignment are based on cl.conserve clustering. 
cl.TRPM8 <- c("N2-RL5-183","N2-RT12-104","N3-RL2-171","N3-RL2-174","N3-RT11-128","N4-RL3-29","N4-RT12-101","N4-RT12-177")
cl.CLTMR <- c("N2-RT12-22","N2-RT12-105","N4-RL3-9","N4-RL3-132","N4-RL3-138","N4-RL3-142","N4-RL3-171","N4-RT12-127","N4-RT12-146")
Un.Gi <- c("N2-RL5-12","N2-RL5-23","N2-RL5-29","N2-RL5-67","N2-RL5-68","N2-RL5-92","N2-RL5-98","N2-RL5-105","N2-RL5-108","N2-RL5-170","N2-RT12-62","N2-RT12-181","N3-RL2-117","N3-RL2-185","N3-RT11-5","N3-RT11-59","N3-RT11-126","N3-RT11-152","N3-RT11-191","N4-RL3-58","N4-RL3-155","N4-RL3-156","N4-RT12-81") 
Ab.LTMR_from_cl3_in_cl.conserv <- c("N2-RL5-26","N2-RL5-165","N2-RT12-32","N2-RT12-47","N2-RT12-80","N2-RT12-85","N3-RL2-162","N3-RT11-95","N3-RT11-182","N4-RT12-110","N4-RT12-184")
## remove selected cells from existing clusters
cl3_cell_new <- cl3_cell
cl9_cell_new <- cl9_cell
cl17_cell_new <- cl17_cell
cl0_cell_new <- cl0_cell
cl2_cell_new <- cl2_cell
cl5_cell_new <- cl5_cell
cl7_cell_new <- cl7_cell
cl13_cell_new <- cl13_cell
cl18_cell_new <- cl18_cell



#cl3_cell_new <- cl3_cell
#cl3_cell_new %in% cl.TRPM8
#cl3_cell_new <- cl3_cell_new[! cl3_cell_new %in% cl.TRPM8]


cl3_cell_new <- cl3_cell_new[! cl3_cell_new %in% cl.TRPM8]
cl9_cell_new <- cl9_cell_new[! cl9_cell_new %in% cl.TRPM8]
cl17_cell_new <- cl17_cell_new[! cl17_cell_new %in% cl.TRPM8]
cl3_cell_new <- cl3_cell_new[! cl3_cell_new %in% cl.CLTMR]
cl0_cell_new <- cl0_cell_new[! cl0_cell_new %in% Un.Gi]
cl2_cell_new <- cl2_cell_new[! cl2_cell_new %in% Un.Gi]
cl3_cell_new <- cl3_cell_new[! cl3_cell_new %in% Un.Gi]
cl5_cell_new <- cl5_cell_new[! cl5_cell_new %in% Un.Gi]
cl7_cell_new <- cl7_cell_new[! cl7_cell_new %in% Un.Gi]
cl13_cell_new <- cl13_cell_new[! cl13_cell_new %in% Un.Gi]
cl18_cell_new <- cl18_cell_new[! cl18_cell_new %in% Un.Gi]
cl3_cell_new <- cl3_cell_new[! cl3_cell_new %in% Ab.LTMR_from_cl3_in_cl.conserv]


```



#Rename clusters (cl.conserv)___new name
```{r}
## cl.Ab.split.2 C0-Propr C1-NP1 C2-PEP.H0 C3-PEP.H0 C4-PEP.H8 C5-Ab.LTMR C6-PEP.H5 C7-Ab.LTMR C8-PEP.H4 C9-PEP1.13 C10-NP1 C11-Ad.LTMR C12-NP3 C13-Ad.LTMR C14-PEP3 C15-PEP.H4.15 C16-NP2 C17-C.LTMR C18-Un.Gi

random_group_labels <- sample(x = c("hATF3","hC.LTMR","hTRPM8","hPropr","hAb.LTMR.s22","hAb.LTMR","hAd.LTMR","hPEP.0","hPEP.NTRK3","hPEP.CHRNA7","hPEP.KIT","hPEP.PIEZOh","hPEP.TRPV1/A1.2","hPEP.TRPV1/A1.1","hPEP.SST","hNP2","hNP1"), size = ncol(x = Seurat.integr.3000), replace = TRUE)
Seurat.integr$cl.conserv_final <- random_group_labels

Seurat.integr$cl.conserv_final[cl0_cell_new] <- "hPropr"
Seurat.integr$cl.conserv_final[cl1_cell] <- "hNP1"
Seurat.integr$cl.conserv_final[cl2_cell_new] <- "hPEP.0"
Seurat.integr$cl.conserv_final[cl3_cell_new] <- "hPEP.0"
Seurat.integr$cl.conserv_final[cl4_cell] <- "hPEP.NTRK3"
Seurat.integr$cl.conserv_final[cl5_cell_new] <- "hAb.LTMR"
Seurat.integr$cl.conserv_final[cl6_cell] <- "hPEP.CHRNA7"
Seurat.integr$cl.conserv_final[cl7_cell_new] <- "hAb.LTMR"
Seurat.integr$cl.conserv_final[cl8_cell] <- "hPEP.PIEZOh"
Seurat.integr$cl.conserv_final[cl9_cell_new] <- "hPEP.TRPV1/A1.1"
Seurat.integr$cl.conserv_final[cl10_cell] <- "hNP1"
Seurat.integr$cl.conserv_final[cl11_cell] <- "hAd.LTMR"
Seurat.integr$cl.conserv_final[cl12_cell] <- "hPEP.SST"
Seurat.integr$cl.conserv_final[cl13_cell_new] <- "hAd.LTMR"
Seurat.integr$cl.conserv_final[cl14_cell] <- "hPEP.KIT"
Seurat.integr$cl.conserv_final[cl15_cell] <- "hPEP.TRPV1/A1.2"
Seurat.integr$cl.conserv_final[cl16_cell] <- "hNP2"
Seurat.integr$cl.conserv_final[cl.CLTMR] <- "hC.LTMR"
Seurat.integr$cl.conserv_final[Un.Gi] <- "hATF3"
Seurat.integr$cl.conserv_final[cl.TRPM8] <- "hTRPM8"
Seurat.integr$cl.conserv_final[Ab.LTMR_from_cl3_in_cl.conserv] <- "hAb.LTMR"


```




```{r}
##conserv_original
Idents(Seurat.integr) <- Seurat.integr$cl.conserv_final

Idents(Seurat.integr) <- factor(x = Idents(Seurat.integr), levels =c("hNP1","hNP2","hPEP.SST","hPEP.TRPV1/A1.1","hPEP.TRPV1/A1.2","hPEP.PIEZOh","hPEP.KIT","hPEP.CHRNA7","hPEP.NTRK3","hPEP.0","hAd.LTMR","hAb.LTMR","hPropr","hC.LTMR","hTRPM8","hATF3"))
```

```{r}
## assign color for each cluster
XX.color.Paired.cl.conserv_final=c('#6666FF','#00a9ff','#8494ff','#c77cff','#ff66b2','#ff9933','#ff68a1','#ff3333','#ed68ed','#dcc66e','#0cb702','#aba300','#7cae00','#FF99FF','#00b8e7','#928e8f')

```


```{r}
DimPlot(Seurat.integr, group.by = "cl.conserv_final",label = F, cols = XX.color.Paired.cl.conserv_final, order = c("hATF3","hTRPM8","hC.LTMR", "hPropr","hAb.LTMR","hAd.LTMR","hPEP.0","hPEP.NTRK3","hPEP.CHRNA7","hPEP.KIT","hPEP.PIEZOh","hPEP.TRPV1/A1.2","hPEP.TRPV1/A1.1","hPEP.SST","hNP2","hNP1"))

```
```{r}
#
Seurat.integr.3000 <- Seurat.integr

```


```{r}
# Save metadata

save(Seurat.integr.3000,HS.counts.raw,Meta.1066.wo.glia,Meta.fused, file = "E:/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Hs_LCM_final_new_name.RData")
```

```{r,fig.height=6, fig.width=12}
## Dotplot itch receptors

## itch receptor ['HRH1','HRH4','MRGPRX1','MRGPRX4','HTR2A','HTR7','F2RL1','MRGPRD','CYSLTR2','IL4R','IL13RA1','IL31RA','OSMR','IL7R','CRLF2','IL1RAP','TLR3','TLR7','JAK1']

DotPlot(Seurat.integr.3000, features = c('HRH1','HRH4','MRGPRX1','MRGPRX4','HTR2A','HTR7','F2RL1','MRGPRD','CYSLTR2','IL4R','IL13RA1','IL31RA','OSMR','IL7R','CRLF2','IL1RAP','TLR3','TLR7','JAK1')) + RotatedAxis() + theme(axis.text = element_text(size = 10))

```

