---
titlC:/E "kinase"
author: "H. Yu"
datC:/E "7/15/2023"
output: html_document
---
#### single soma

#### generate kinase expression data frame from different datasets based on raw count gene expression matrix
```{r, fig.width=10, fig.height=30}
drg <-
  read.csv("C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/human_drg_somaseq_rawcounts.csv",header=TRUE)

rows_to_remove <- grepl("\\.", drg$Gene_ID)

drg <- drg[!rows_to_remove, ]

drg <- drg[!duplicated(drg$Gene_ID), ]

rownames <- drg[, 1]
drg <- drg[, -1]
row.names(drg) <- rownames

# Select all kinase according to Gene Ontology
kinase_list <-
  biomaRt::getBM(
    filters = "go",
    attributes = c("ensembl_gene_id", "hgnc_symbol","description"),
    values = c('GO:0004896','GO:0004950'),
    mart = biomaRt::useDataset("hsapiens_gene_ensembl", biomaRt::useMart("ensembl"))
  )

#kinase list
drg_kinase=c()
for(i in c(kinase_list$hgnc_symbol))
  if (i %in% row.names(drg))
    drg_kinase=c(drg_kinase,i)

drg_cluster <- drg[drg_kinase,]


# Calculate row sums
row_sums <- rowSums(drg_cluster)

# Identify rows where the sum is 0
zero_rows <- row_sums == 0

# Remove those rows
drg_cluster <- drg_cluster[!zero_rows, ]

rows_to_remove <- grepl("\\.", rownames(drg_cluster))
drg_cluster<- drg_cluster[!rows_to_remove, ]


write.csv(drg_cluster,"C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/kinase_somaseq_rawcounts.csv")
```


#### Select effective kinase expression 
```{r}

## To remove low expression kinase either with low count or low percentage in all cells and keep effective detection kinase, introduce two parameters
Detect_number_greater_than = 0  ## (parameter for low count threshold)
Percentage = 0.01 ## (parameter for low percentage in all cells)



## read raw count gene expression matrix
drg_cluster <- read.csv("C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/kinase_somaseq_rawcounts.csv")


## Select effective detected kinase
# Initialize a vector to hold the count for each row
count_values_greater_than_zero <- numeric(nrow(drg_cluster))
# Loop over each row
for (i in 1:nrow(drg_cluster)) {
  # Count the number of values in the i-th row that are greater than 0 and store it in the vector
  count_values_greater_than_zero[i] <- sum(drg_cluster[i,] > Detect_number_greater_than)
}
num_columns <- ncol(drg_cluster)
detection_index = count_values_greater_than_zero/num_columns
effective_detection_kinase_number=count(detection_index >= Percentage)
single_soma <- drg_cluster[detection_index >= Percentage, "X"]

## print the total number of effective detected kinase and save as csv file
print(paste("effective_kinase_number:", effective_detection_kinase_number[2,2]))
print(single_soma)
write.csv(single_soma,"C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/single_soma_kinase.csv")

```




#### single nucleus
```{r, fig.width=10, fig.height=30}
drg <-
  read.csv("C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/human_drg_nucleuseq_rawcounts.csv",header=TRUE)

rows_to_remove <- grepl("\\.", drg$Gene_ID)

drg <- drg[!rows_to_remove, ]

drg <- drg[!duplicated(drg$Gene_ID), ]

rownames <- drg[, 1]
drg <- drg[, -1]
row.names(drg) <- rownames

# Select all kinases according to Gene Ontology
kinase_list <-
  biomaRt::getBM(
    filters = "go",
    attributes = c("ensembl_gene_id", "hgnc_symbol","description"),
    values = c('GO:0004896','GO:0004950'),
    mart = biomaRt::useDataset("hsapiens_gene_ensembl", biomaRt::useMart("ensembl"))
  )

#kinase list
drg_kinase=c()
for(i in c(kinase_list$hgnc_symbol))
  if (i %in% row.names(drg))
    drg_kinase=c(drg_kinase,i)

drg_cluster <- drg[drg_kinase,]


# Calculate row sums
row_sums <- rowSums(drg_cluster)

# Identify rows where the sum is 0
zero_rows <- row_sums == 0

# Remove those rows
drg_cluster <- drg_cluster[!zero_rows, ]

rows_to_remove <- grepl("\\.", rownames(drg_cluster))
drg_cluster<- drg_cluster[!rows_to_remove, ]


write.csv(drg_cluster,"C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/kinase_nucleuseq_rawcounts.csv")
```


#### Select effective kinase expression 
```{r}

## To remove low expression kinase either with low count or low percentage in all cells and keep effective detection kinase, introduce two parameters
Detect_number_greater_than = 0  ## (parameter for low count threshold)
Percentage = 0.01 ## (parameter for low percentage in all cells)



## read raw count gene expression matrix
drg_cluster <- read.csv("C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/kinase_nucleuseq_rawcounts.csv")


## Select effective detected kinase
# Initialize a vector to hold the count for each row
count_values_greater_than_zero <- numeric(nrow(drg_cluster))
# Loop over each row
for (i in 1:nrow(drg_cluster)) {
  # Count the number of values in the i-th row that are greater than 0 and store it in the vector
  count_values_greater_than_zero[i] <- sum(drg_cluster[i,] > Detect_number_greater_than)
}
num_columns <- ncol(drg_cluster)
detection_index = count_values_greater_than_zero/num_columns
effective_detection_kinase_number=count(detection_index >= Percentage)
single_nucleus <- drg_cluster[detection_index >= Percentage, "X"]

## print the total number of effective detected kinase and save as csv file
print(paste("effective_kinase_number:", effective_detection_kinase_number[2,2]))
print(single_nucleus)
write.csv(single_nucleus,"C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/single_nucleus_kinase.csv")

```

#### spatial
```{r, fig.width=10, fig.height=30}
drg <-
  read.csv("C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/human_drg_spatialseq_rawcounts.csv",header=TRUE)

rows_to_remove <- grepl("\\.", drg[,1])

drg <- drg[!rows_to_remove, ]

drg <- drg[!duplicated(drg[,1]), ]

rownames <- drg[, 1]
drg <- drg[, -1]
row.names(drg) <- rownames

# Select all kinases according to Gene Ontology
kinase_list <-
  biomaRt::getBM(
    filters = "go",
    attributes = c("ensembl_gene_id", "hgnc_symbol","description"),
    values = c('GO:0004896','GO:0004950'),
    mart = biomaRt::useDataset("hsapiens_gene_ensembl", biomaRt::useMart("ensembl"))
  )

#kinase list
drg_kinase=c()
for(i in c(kinase_list$hgnc_symbol))
  if (i %in% row.names(drg))
    drg_kinase=c(drg_kinase,i)

drg_cluster <- drg[drg_kinase,]


# Calculate row sums
row_sums <- rowSums(drg_cluster)

# Identify rows where the sum is 0
zero_rows <- row_sums == 0

# Remove those rows
drg_cluster <- drg_cluster[!zero_rows, ]

rows_to_remove <- grepl("\\.", rownames(drg_cluster))
drg_cluster<- drg_cluster[!rows_to_remove, ]


write.csv(drg_cluster,"C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/kinase_spatialseq_rawcounts.csv")
```


#### Select effective kinase expression 
```{r}

## To remove low expression kinase either with low count or low percentage in all cells and keep effective detection kinase, introduce two parameters
Detect_number_greater_than = 0  ## (parameter for low count threshold)
Percentage = 0.01 ## (parameter for low percentage in all cells)



## read raw count gene expression matrix
drg_cluster <- read.csv("C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/kinase_spatialseq_rawcounts.csv")


## Select effective detected kinase
# Initialize a vector to hold the count for each row
count_values_greater_than_zero <- numeric(nrow(drg_cluster))
# Loop over each row
for (i in 1:nrow(drg_cluster)) {
  # Count the number of values in the i-th row that are greater than 0 and store it in the vector
  count_values_greater_than_zero[i] <- sum(drg_cluster[i,] > Detect_number_greater_than)
}
num_columns <- ncol(drg_cluster)
detection_index = count_values_greater_than_zero/num_columns
effective_detection_kinase_number=count(detection_index >= Percentage)
spatial <- drg_cluster[detection_index >= Percentage, "X"]

## print the total number of effective detected kinase and save as csv file
print(paste("effective_kinase_number:", effective_detection_kinase_number[2,2]))
print(spatial)
write.csv(spatial,"C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/spatial_kinase.csv")

```


### identify the kinase epxression difference in different dataset 

```{r}

## read data
single_soma_list <- read.csv("C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/single_soma_kinase.csv")
single_nucleus_list <- read.csv("C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/single_nucleus_kinase.csv")
spatial_list <- read.csv("C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/spatial_kinase.csv")

single_soma <- c(single_soma_list[,2])
single_nucleus <- c(single_nucleus_list[,2])
spatial<- c(spatial_list[,2])

# Elements in both single_soma, single_nucleus, and spatial
in_single_soma_single_nucleus_spatial <- Reduce(intersect, list(single_soma, single_nucleus, spatial))
cat("Elements in both single_soma, single_nucleus, and spatial:\n")
print(in_single_soma_single_nucleus_spatial)
cat("Total:", length(in_single_soma_single_nucleus_spatial), "\n\n")

# Elements in single_soma and single_nucleus but not in spatial
in_single_soma_single_nucleus_not_spatial <- setdiff(intersect(single_soma, single_nucleus), spatial)
cat("Elements in both single_soma, single_nucleus, but not spatial:\n")
print(in_single_soma_single_nucleus_not_spatial)
cat("Total:", length(in_single_soma_single_nucleus_not_spatial), "\n\n")


# Elements in single_soma and spatial but not in single_nucleus
in_single_soma_spatial_not_single_nucleus <- setdiff(intersect(single_soma, spatial), single_nucleus)
cat("Elements in both single_soma,spatial , but not single_nucleus:\n")
print(in_single_soma_spatial_not_single_nucleus)
cat("Total:", length(in_single_soma_spatial_not_single_nucleus), "\n\n")



# Elements in single_nucleus and spatial but not in single_soma
in_single_nucleus_spatial_not_single_soma <- setdiff(intersect(single_nucleus, spatial), single_soma)
cat("Elements in both  spatial, single_nucleus but not single_soma:\n")
print(in_single_nucleus_spatial_not_single_soma)
cat("Total:", length(in_single_nucleus_spatial_not_single_soma), "\n\n")

# Elements specific in single_soma
specific_single_soma <- setdiff(single_soma, union(single_nucleus, spatial))
cat("Elements specific in single_soma:\n")
print(specific_single_soma)
cat("Total:", length(specific_single_soma), "\n\n")

# Elements specific in single_nucleus
specific_single_nucleus <- setdiff(single_nucleus, union(single_soma, spatial))
cat("Elements specific in single_nucleus:\n")
print(specific_single_nucleus)
cat("Total:", length(specific_single_nucleus), "\n\n")

# Elements specific in spatial
specific_spatial <- setdiff(spatial, union(single_soma, single_nucleus))
cat("Elements specific in spatial:\n")
print(specific_spatial)
cat("Total:", length(specific_spatial), "\n\n")

# Elements in both single_soma and single_nucleus
in_single_soma_single_nucleus <- intersect(single_soma, single_nucleus)
cat("Elements in both single_soma and single_nucleus:\n")
print(in_single_soma_single_nucleus)
cat("Total:", length(in_single_soma_single_nucleus), "\n\n")

# Elements in both single_soma and spatial
in_single_soma_spatial <- intersect(single_soma, spatial)
cat("Elements in both single_soma and spatial:\n")
print(in_single_soma_spatial)
cat("Total:", length(in_single_soma_spatial), "\n\n")

# Elements in both single_nucleus and spatial
in_single_nucleus_spatial <- intersect(single_nucleus, spatial)
cat("Elements in both single_nucleus and spatial:\n")
print(in_single_nucleus_spatial)
cat("Total:", length(in_single_nucleus_spatial), "\n\n")


```



#### Heatmap to show the kinase expression difference in different datasets
```{r}
## All kinases detected in each three datasets
## read data
single_soma_list <- read.csv("C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/single_soma_kinase.csv")
single_nucleus_list <- read.csv("C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/single_nucleus_kinase.csv")
spatial_list <- read.csv("C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/spatial_kinase.csv")

single_soma <- c(single_soma_list[,2])
single_nucleus <- c(single_nucleus_list[,2])
spatial<- c(spatial_list[,2])

merged_unique_elements <- Reduce(union, list(single_soma, single_nucleus, spatial))


```

```{r}

## single soma 

drg_cluster <- read.csv("C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/kinase_somaseq_rawcounts.csv")


# Get the names of all columns in drg_cluster
all_columns <- names(drg_cluster)

# For each element in single_soma
for(element in merged_unique_elements){
  
  # If the element is not in column X of drg_cluster
  if(!(element %in% drg_cluster$X)){
    
    # Create a new row where the value in column X is the element and all other columns are 0
    new_row <- setNames(data.frame(matrix(ncol = length(all_columns), nrow = 1)), all_columns)
    new_row$X <- element
    new_row[,-which(names(new_row)=="X")] <- 0
    
    # Add the new row to drg_cluster
    drg_cluster <- rbind(drg_cluster, new_row)
  }
}

write.csv(drg_cluster,"C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/Heatmap/kinase_somaseq_rawcounts_common.csv")

single_soma <- read.csv("C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/Heatmap/kinase_somaseq_rawcounts_common.csv")

selected_rows <- single_soma[single_soma$X %in% merged_unique_elements, ]

write.csv(selected_rows,"C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/Heatmap/kinase_somaseq_rawcounts_heatmap.csv")


```


```{r}

#single nucleus
drg_cluster <- read.csv("C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/kinase_nucleuseq_rawcounts.csv")


# Get the names of all columns in drg_cluster
all_columns <- names(drg_cluster)

# For each element in single_nucleus
for(element in merged_unique_elements){
  
  # If the element is not in column X of drg_cluster
  if(!(element %in% drg_cluster$X)){
    
    # Create a new row where the value in column X is the element and all other columns are 0
    new_row <- setNames(data.frame(matrix(ncol = length(all_columns), nrow = 1)), all_columns)
    new_row$X <- element
    new_row[,-which(names(new_row)=="X")] <- 0
    
    # Add the new row to drg_cluster
    drg_cluster <- rbind(drg_cluster, new_row)
  }
}

write.csv(drg_cluster,"C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/Heatmap/kinase_nucleuseq_rawcounts_common.csv")

single_nucleus <- read.csv("C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/Heatmap/kinase_nucleuseq_rawcounts_common.csv")

selected_rows <- single_nucleus[single_nucleus$X %in% merged_unique_elements, ]

write.csv(selected_rows,"C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/Heatmap/kinase_nucleuseq_rawcounts_heatmap.csv")
```


```{r}

#spatial
drg_cluster <- read.csv("C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/kinase_spatialseq_rawcounts.csv")


# Get the names of all columns in drg_cluster
all_columns <- names(drg_cluster)

# For each element in sptial
for(element in merged_unique_elements){
  
  # If the element is not in column X of drg_cluster
  if(!(element %in% drg_cluster$X)){
    
    # Create a new row where the value in column X is the element and all other columns are 0
    new_row <- setNames(data.frame(matrix(ncol = length(all_columns), nrow = 1)), all_columns)
    new_row$X <- element
    new_row[,-which(names(new_row)=="X")] <- 0
    
    # Add the new row to drg_cluster
    drg_cluster <- rbind(drg_cluster, new_row)
  }
}

write.csv(drg_cluster,"C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/Heatmap/kinase_sptial_rawcounts_common.csv")

sptial <- read.csv("C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/Heatmap/kinase_sptial_rawcounts_common.csv")

selected_rows <- sptial[sptial$X %in% merged_unique_elements, ]

write.csv(selected_rows,"C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/Heatmap/kinase_sptial_rawcounts_heatmap.csv")

```


#### generate heatmap
```{r}
##

# Read the CSV files into data frames
single_soma <- read.csv("C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/Heatmap/kinase_somaseq_rawcounts_heatmap.csv")
single_nucleus <- read.csv("C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/Heatmap/kinase_nucleuseq_rawcounts_heatmap.csv")
spatial <- read.csv("C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Final analysis for publication/Drug target heat map/database comparison/Heatmap/kinase_sptial_rawcounts_heatmap.csv")

# Set the row names to be the values in the first columns
row.names(single_soma) <- single_soma$X
row.names(single_nucleus) <- single_nucleus$X
row.names(spatial) <- spatial$X

# Remove the first columns
single_soma <- subset(single_soma, select = -c(X, X.1))
single_nucleus <- subset(single_nucleus, select = -c(X, X.1))
spatial <- subset(spatial, select = -c(X, X.1))


# Calculate the row means and create new data frames
single_soma_means <- data.frame(RowName = row.names(single_soma), Mean = rowMeans(single_soma, na.rm = TRUE))
single_nucleus_means <- data.frame(RowName = row.names(single_nucleus), Mean = rowMeans(single_nucleus, na.rm = TRUE))
spatial_means <- data.frame(RowName = row.names(spatial), Mean = rowMeans(spatial, na.rm = TRUE))


# Merge the three mean data frames into one based on the row names
combined_means <- merge(single_soma_means, single_nucleus_means, by = "RowName", all = TRUE)
combined_means <- merge(combined_means, spatial_means, by = "RowName", all = TRUE)

# Print the combined mean data frame
print(combined_means)

# Assume AA, BB, and CC are your data frames

# Rename the "Mean" column for each data frame
names(single_soma_means)[names(single_soma_means) == "Mean"] <- "single_soma"
names(single_nucleus_means)[names(single_nucleus_means) == "Mean"] <- "single_nucleus"
names(spatial_means)[names(spatial_means) == "Mean"] <- "spatial"

# Merge the data frames based on the "RowName" column
merged_AB <- merge(single_soma_means, single_nucleus_means, by = "RowName", all = TRUE)
merged_ABC <- merge(merged_AB, spatial_means, by = "RowName", all = TRUE)

# Print the merged data frame
print(merged_ABC)
```


#### heatmap strategy 1

```{r}
# Load the dplyr package
library(dplyr)

# Rank the data frame based on the single soma sequencing
merged_ABC <- merged_ABC %>%
  arrange(desc(single_soma))


## nomalization

AA <- merged_ABC

# Change the first column to row names
rownames(AA) <- AA[, 1]

# Remove the first column
AA <- AA[, -1]

# Change the values to their base 2 logarithms
AA <- log2(AA+1)

# Print the transformed data frame
#print(AA)

```

```{r}
# nomalize column max to 1

AA_normalized <- AA

# Use apply() to iterate over each column (MARGIN = 2)
AA_normalized <- apply(AA, MARGIN = 2, function(x) x / max(x))

# Convert the matrix result back to a data frame
AA_normalized <- as.data.frame(AA_normalized)

# Print the normalized data frame
print(AA_normalized)

```


```{r, fig.width=16, fig.height=40}

AA_heatmap <-data.matrix(AA_normalized[0:100,])

lmat = rbind(c(0,4),c(3,1),c(0,2))
lwid = c(1,5)
lhei = c(0.1,2.5,0.5)

heatmap.2(as.matrix(AA_heatmap), dendrogram = 'both', Colv = FALSE, Rowv = FALSE, scale = "none", col = bluered(100), trace = "none", density.info = "none",  keysize=0.05, key.title=NA, lmat = lmat, lwid = lwid, lhei = lhei)


```


##Supplementary Figure 7A

```{r, fig.width=16, fig.height=40}

AA_heatmap <-data.matrix(AA_normalized[0:100,])

lmat = rbind(c(0,4),c(3,1),c(0,2))
lwid = c(1,5)
lhei = c(0.1,2.5,0.5)

# Set up the SVG device
svg(filename = "C:/E/Posdoc work at Upenn/Lab_work/Projected_I_am_intersted_in/Transcriptome of human DRG neurons/Manuscript and figs/Submmision/Nature neuroscience/Final/Revision/Resubmission/20240716_Final/new_plot/SF9A_3.svg", width = 16, height = 40)

heatmap.2(as.matrix(AA_heatmap), dendrogram = 'both', Colv = FALSE, Rowv = FALSE, scale = "none", col = bluered(100), trace = "none", density.info = "none",  keysize=0.05, key.title=NA, lmat = lmat, lwid = lwid, lhei = lhei)

# Close the SVG device
dev.off()
```


